Summarize twas: chr22

### 2020-08-07 analysis/simulation-multi-ukbchr17to22-gtex.adipose.Rmd
visual chr17to22
Remove ignored files
susie names

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message= F)
```

@@

Results for 10 simulations runs, using different initiate and update strategy

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message= F, warning = F)
```

@@

Results for 10 simulations runs, using different initialize and update strategy

### 2020-08-07 analysis/simulation-multi-ukbchr22-gtex.adipose2.Rmd
Remove ignored files
susie names

# Mr.ash2 parameter estimation
Results for 9 simulations runs, using different initiate and update strategy
```{r param function}
show_param <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  parf <- lapply(f, '[[', "par")
  param <- do.call(rbind, lapply(parf, function(x) t(read.table(x))[2:1,]))
  truth <- param[1:(nrow(param)/2)*2-1,]
  est <- param[1:(nrow(param)/2)*2,]
  outdt <- matrix(0, ncol = 2*ncol(param), nrow = nrow(param)/2)
  outdt[,c(1,3,5,7)] <- truth
  outdt[,c(2,4,6,8)] <- est
  outdt <-cbind(1:nrow(outdt),outdt)
  colnames(outdt) <- c("Simulation#", paste0(rep(c("Truth","Est."),4)))
  knitr::kable(outdt) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "Gene.pi1" = 2, "Gene.PVE" = 2, "SNP.pi1" = 2, "SNP.PVE" =2))
}
```

>>>>

# Mr.ash2 parameter estimation
Results for 9 simulations runs, using different initialize and update strategy
```{r param function}
show_param <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  parf <- lapply(f, '[[', "par")
  param <- do.call(rbind, lapply(parf, function(x) t(read.table(x))[2:1,]))
  truth <- param[1:(nrow(param)/2)*2-1,]
  est <- param[1:(nrow(param)/2)*2,]
  outdt <- matrix(0, ncol = 2*ncol(param), nrow = nrow(param)/2)
  outdt[,c(1,3,5,7)] <- truth
  outdt[,c(2,4,6,8)] <- est
  outdt <-cbind(1:nrow(outdt),outdt)
  colnames(outdt) <- c("Simulation#", paste0(rep(c("Truth","Est."),4)))
  knitr::kable(outdt) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "Gene.pi1" = 2, "Gene.PVE" = 2, "SNP.pi1" = 2, "SNP.PVE" =2))
}
```
